---
title: "Plotting contour plots from water column stations"
author: "Helene"
date: "18 Feb 2022"
output: github_document:
    toc: true
  html_document:
    toc: true    
    toc_float: true
    code_folding: hide
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_format = "all", output_dir = "../Produced_documents") })

---

* NB uses cleaned datset made in script "Read_and_check_AqM_files.Rmd".

## 0. Libraries
```{r, error = F, warning = F}

# clean workspace
rm(list=ls())

#library (caTools)
library (lubridate)
library (dplyr)
#install.packages ("vctrs")
#install.packages ("ellipsis")
#library (vctrs)
#library (ellipsis)
library(tidyr)     # 
#library(purrr)     # for map_dbl
#install.packages ("rMR")
#library (rMR) # calculate O2 saturation
#library (seacarb)
library(akima) # for interpolations
library(ggplot2)
library(readxl)
library(mgcv)     # for gam() in plots
library(patchwork) # for arranging plots in panels
library(tidyverse)
library(scales)

library(RColorBrewer)
# specific functions needed for the contour plots

# NB! this source file contains the function (used by okokyst_plot function here), and needs to be saved in the same folder as this script

source("okokyst_plot_functions_LOV.R")# new version in 2021

# Use a self-defined color scale  
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

colors <- rev(brewer.pal(10, "RdYlBu"))
rgb.palette <- colorRampPalette(colors)

```


## 1. Read and clean files
### a. read
* this file is produced in script "Read_and_check_OKOKYST_Klima.Rmd"
```{r}

# clear workspace
rm(list = ls())

#dir("Datasett")

df <- read.delim ("Datasett/OKOKYST_data_cleaned_Nhs_NH4cleaned.txt")

#str(df)

# convert back to Date
df$Date <- as.Date(df$Date, "%d.%m.%Y")
#str(df)

# station naming, convert back to factor
#df$StationId <- as.factor (df$StationId)



#find out where in the dataset there is high extreme values
extreme_values <- df %>% filter((TOTN > 900) | (SIO2 > 2400) | (TOTP > 100) | (NH4 > 400))
#remove the extreme values from dataset
df <- df %>% filter(((TOTN < 800)  %>% replace_na(TRUE)) , ((SIO2  < 2000) %>% replace_na(TRUE)) , ((TOTP < 100)%>% replace_na(TRUE)) , ((NH4 < 400)%>% replace_na(TRUE)))

#select years
df <- subset(df, Date >= "2017-01-01" &  Date <= "2021-11-30")

```

### b. Clean data for contour plots, summarizing for depths
* the interpolation in okokyst_plot() does not like a lot of missing data. so I make a dataset that has only the 5 depths for disceret stations (0-30m), average the dataset for those depths, and make on separate dataset for each station. this can probably be done in many different ways, but I found this works for me... 
```{r}

#str (df)

# For water chemistry variables with discrete depths (0-30m), NB! you need to replace with the column names in the file you use!  remove NA values
df_chem <- df %>%
  select(-Depth2)  %>%
   #filter (Depth1 == 0 | Depth1 == 5| Depth1 == 10 | Depth1 == 20 | Depth1 == 30) %>%
   rename (Depth = Depth1) 



# make df for each station, NB replace with the stations you use (needed for okokyst_plot function)

VT71 <- df_chem %>%
  filter(StationId == "VT71")

VR51 <- df_chem %>%
  filter(StationId == "VR51")

VR31 <- df_chem %>%
  filter(StationId == "VR31")

VR61 <- df_chem %>%
  filter(StationId == "VR61")

VR52 <- df_chem %>%
  filter(StationId == "VR52")





```

## 2. Contour plots

### o. example from Dag 13.04.2021 - just for showing differnt functionality and testing
```{r}
## Using okokyst_plot() function ---- 

# Basic plot
# debugonce(okokyst_plot)
okokyst_plot(VR54, "DOC")

# Don't show the coloured points (can instead use 'colored_points_size' to adjust size)
okokyst_plot(VR54, "KlfA", colored_points = FALSE)

# If you want to remove part of the background colors, then
# (1) first use okokyst_make_plotdata()  (here, we call the result 'my_plotdata')
# (2) select the part of the data and store the result (here, called 'sel')
# (3) set the variable 'z' in the dataset from 1 ('my_plotdata') to be NA for all selected rows ('sel')
# (4) use okokyst_plot() as before, but set plotdata = the name of the dataset from 1 (here, 'my_plotdata') 
# Example:
my_plotdata <- okokyst_make_plotdata(df2, "KlfA")  
sel <- with(my_plotdata, Time >= dmy("01.05.2020") & Time <= dmy("31.05.2020") & Depth < 15)
my_plotdata$z[sel] <- NA
okokyst_plot(df2, "KlfA", plotdata = my_plotdata)

# Try GAM (doesn't work well in this case)
okokyst_plot(VR54, "KlfA", gam = TRUE, gam_k = 5)

# Try a different palette (you can set palette = 'A', 'B', 'C' or 'D' - the default is D)
okokyst_plot(VR54, "KlfA", palette = "C")

# Turn colors "upside down" (setting colored_points_rim = TRUE to see points in all parts)
okokyst_plot(VR54, "KlfA", palette = "A", 
             reverse_colors = TRUE, colored_points_rim = TRUE)

okokyst_plot(VR54, "KlfA") +
  scale_fill_gradientn(colours = jet.colors(16))

```



### a. Here is an example for NO3 for two stations, this can of course be adapted for all different stations/variables

#### VT71 TOTN
```{r}

# check range, can be set automatically, but I often found the plot looks nicer if you set manually
quantile(VT71$TOTN, na.rm = T)

# with colored points and date label every 2nd month (depends on length of the timeseries for the station)
# NB! here I set the labels = null (compare with VT71 below), because I want to have them on top of eachother in a panel (see 3. Combine figures below)

grenser <- c(0,500)
VT71_TOTN <- okokyst_plot(data = VT71, varname = "TOTN", ctd_variable = F,
                   colored_points = T, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTN", colours = jet.colors(20), limits= grenser, breaks = c(100,200,300,400), oob=squish) +
                    scale_x_datetime(date_breaks = "4 month", labels =  NULL)

VT71_TOTN

#ggsave ("Figures/VT71/VT71_TOTN.png", dpi=500, width = 8, height = 3)


```



#### VT71 NO3
```{r}

quantile (VT71$NO3_NO2, na.rm = T)

# med punkter

grenser <- c(0,200)
VT71_NO3 <- okokyst_plot(data = VT71, varname = "NO3_NO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits =grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NO"[3]* "+ NO"[2]), colours = jet.colors(16),limits=grenser, breaks = c(50,100,150), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", labels =  NULL)

VT71_NO3

#ggsave ("Figures/VT71/VT71_NO3.png", dpi=500, width = 8, height = 3)
 
```
#### VT71 NH4
```{r}

quantile (VT71$NH4, na.rm = T)

# med punkter
grenser <- c(0,80)
VT71_NH4 <- okokyst_plot(data = VT71, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NH"[4]), limit=grenser, colours = jet.colors(16), breaks = c(20,40,60), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT71_NH4

#ggsave ("Figures/VT71/VT71_NH4.png", dpi=500, width = 8, height = 3)


```


####


## 3. Combine figures (with patchwork library)
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
Nitrogen <- VT71_TOTN +  VT71_NO3 + VT71_NH4 + plot_layout(ncol = 1, width = 8, height =6)
plot (Nitrogen)
  ggsave("Figures/VT71/VT71_nitrogen_panel_longtimeseries.png", plot = Nitrogen,  width = 8, height = 6)
  
```

####VT71 PO4

```{r}

quantile (VT71$PO4, na.rm = T)

# med punkter

grenser <- c(0,60)
VT71_PO4 <- okokyst_plot(data = VT71, varname = "PO4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("PO"[4]), colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", labels =  NULL)
 
                      #theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))

VT71_PO4

#ggsave ("Figures/VT71/VT71_PO4.png", dpi=500, , width = 8, height = 3)
```

####VT71 TOTP
```{r}
quantile (VT71$TOTP, na.rm = T)

# med punkter

grenser <- c(0,60)
VT71_TOTP <- okokyst_plot(data = VT71, varname = "TOTP", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTP", colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VT71_TOTP

#ggsave ("Figures/VT71/VT71_TOTP.png", dpi=500, width = 8, height = 3)
```


####VT71 SIO2

```{r}

quantile (VT71$SIO2, na.rm = T)

# med punkter
grenser <- c(0,900)
VT71_SIO2 <- okokyst_plot(data = VT71, varname = "SIO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("SiO"[2]), colours = jet.colors(16),limits=grenser,breaks = c(200,400,600,800), oob=squish ) +
                       scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT71_SIO2

#ggsave ("Figures/VT71/VT71_SIO2.png", dpi=500, width = 8, height = 3)

```

##cOMBINE 
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
VT71_fosfat_Si <- VT71_TOTP +  VT71_PO4 + VT71_SIO2 +  plot_layout(ncol = 1,  width = 8, height = 6)
plot (VT71_fosfat_Si)
ggsave("Figures/VT71/VT71_fosfat_Si_panel_longtimeserie.png", plot = VT71_fosfat_Si,  width = 8, height = 6)
```
  

#### VT71 klfa


```{r}
quantile (VT71$KlfA, na.rm = T)

# med punkter
grenser <- c(0,5)
VT71_KlfA <- okokyst_plot(data = VT71, varname = "KlfA", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                      scale_fill_gradientn("KlfA", colours = jet.colors(16),limits=grenser, breaks = c(1,2,3,4), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT71_KlfA 

ggsave ("Figures/VT71/VT71_KlfA_longtimeserie.png" , width = 8, height = 3)
```



#### VR51 TOTN

```{r}

# check range, can be set automatically, but I often found the plot looks nicer if you set manually
quantile(VR51$TOTN, na.rm = T)

# with colored points and date label every 2nd month (depends on length of the timeseries for the station)
# NB! here I set the labels = null (compare with VT71 below), because I want to have them on top of eachother in a panel (see 3. Combine figures below)

grenser <- c(0,500)
VR51_TOTN <- okokyst_plot(data = VR51, varname = "TOTN", ctd_variable = F,
                   colored_points = T, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTN", colours = jet.colors(20), limits= grenser, breaks = c(100,200,300,400), oob=squish) +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR51_TOTN

ggsave ("Figures/VR51/VR51_TOTN.png", dpi=500, width = 8, height = 3)


```



#### VR51 NO3
```{r}

quantile (VR51$NO3_NO2, na.rm = T)

# med punkter

grenser <- c(0,200)
VR51_NO3 <- okokyst_plot(data = VR51, varname = "NO3_NO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits =grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NO"[3]* "+ NO"[2]), limits=grenser,colours = jet.colors(16), breaks = c(50,100,150), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR51_NO3

ggsave ("Figures/VR51/VR51_NO3.png", dpi=500, width = 8, height = 3)
 
```
#### VR51 NH4
```{r}

quantile (VR51$NH4, na.rm = T)

# med punkter
grenser <- c(0,80)
VR51_NH4 <- okokyst_plot(data = VR51, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NH"[4]), limit=grenser, colours = jet.colors(16), breaks = c(20,40,60), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR51_NH4

ggsave ("Figures/VR51/VR51_NH4.png", dpi=500, width = 8, height = 3)


```


####


## 3. Combine figures (with patchwork library)
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
Nitrogen <- VR51_TOTN +  VR51_NO3 + VR51_NH4 + plot_layout(ncol = 1, width = 8, height =6)
plot (Nitrogen)
  ggsave("Figures/VR51/VR51_nitrogen_panel_test.png", plot = Nitrogen,  width = 8, height = 6)
  
```

####VR51 PO4

```{r}

quantile (VR51$PO4, na.rm = T)

# med punkter

grenser <- c(0,60)
VR51_PO4 <- okokyst_plot(data = VR51, varname = "PO4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("PO"[4]), colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)
 
                      #theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))

VR51_PO4

ggsave ("Figures/VR51/VR51_PO4.png", dpi=500, , width = 8, height = 3)
```

####VR51 TOTP
```{r}
quantile (VR51$TOTP, na.rm = T)

# med punkter

grenser <- c(0,60)
VR51_TOTP <- okokyst_plot(data = VR51, varname = "TOTP", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTP", colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR51_TOTP

ggsave ("Figures/VR51/VR51_TOTP.png", dpi=500, width = 8, height = 3)
```


####VR51 SIO2

```{r}

quantile (VR51$SIO2, na.rm = T)
rm
# med punkter
grenser <- c(0,900)
VR51_SIO2 <- okokyst_plot(data = VR51, varname = "SIO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("SiO"[2]), colours = jet.colors(16),limits=grenser,breaks = c(200,400,600,800), oob=squish ) +
                       scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR51_SIO2

ggsave ("Figures/VR51/VR51_SIO2.png", dpi=500, width = 8, height = 3)

```

##cOMBINE 
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
VR51_fosfat_Si <- VR51_TOTP +  VR51_PO4 + VR51_SIO2 +  plot_layout(ncol = 1,  width = 8, height = 6)
plot (VR51_fosfat_Si)
ggsave("Figures/VR51/VR51_fosfat_Si_panel.png", plot = VR51_fosfat_Si,  width = 8, height = 6)
```
  

#### VR51 klfa
```{r}
quantile (VR51$KlfA, na.rm = T)

# med punkter
grenser <- c(0,5)
VR51_KlfA <- okokyst_plot(data = VR51, varname = "KlfA", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                      scale_fill_gradientn("KlfA", colours = jet.colors(16),limits=grenser, breaks = c(1,2,3,4), oob=squish) +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR51_KlfA 

ggsave ("Figures/VR51/VR51_KlfA.png" , width = 8, height = 3)
```



#### VR31 TOTN
```{r}

# check range, can be set automatically, but I often found the plot looks nicer if you set manually
quantile(VR31$TOTN, na.rm = T)

# with colored points and date label every 2nd month (depends on length of the timeseries for the station)
# NB! here I set the labels = null (compare with VT71 below), because I want to have them on top of eachother in a panel (see 3. Combine figures below)

grenser <- c(0,500)
VR31_TOTN <- okokyst_plot(data = VR31, varname = "TOTN", ctd_variable = F,
                   colored_points = T, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTN", colours = jet.colors(20), limits= grenser, breaks = c(100,200,300,400), oob=squish) +
                    scale_x_datetime(date_breaks = "4 month", labels =  NULL)

VR31_TOTN

#ggsave ("Figures/VR31/VR31_TOTN.png", dpi=500, width = 8, height = 3)


```



#### VR31 NO3
```{r}

quantile (VR31$NO3_NO2, na.rm = T)

# med punkter

grenser <- c(0,200)
VR31_NO3 <- okokyst_plot(data = VR31, varname = "NO3_NO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits =grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NO"[3]* "+ NO"[2]), colours = jet.colors(16), limits=grenser,breaks = c(50,100,150), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", labels =  NULL)

VR31_NO3

#ggsave ("Figures/VR31/VR31_NO3.png", dpi=500, width = 8, height = 3)
 
```
#### VR31 NH4
```{r}

quantile (VR31$NH4, na.rm = T)

# med punkter
grenser <- c(0,80)
VR31_NH4 <- okokyst_plot(data = VR31, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NH"[4]), limit=grenser, colours = jet.colors(16), breaks = c(20,40,60), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR31_NH4

ggsave ("Figures/VR31/VR31_NH4_2014_2021_withoutjan_mars_2021.png", dpi=500, width = 8, height = 3)


```


####


## 3. Combine figures (with patchwork library)
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
Nitrogen <- VR31_TOTN +  VR31_NO3 + VR31_NH4 + plot_layout(ncol = 1, width = 8, height =6)
plot (Nitrogen)
  ggsave("Figures/VR31/VR31_nitrogen_panel_longtimeserie_without_jan_mars_2021_NH4.png", plot = Nitrogen,  width = 8, height = 6)
  
```

####VR31 PO4

```{r}

quantile (VR31$PO4, na.rm = T)

# med punkter

grenser <- c(0,60)
VR31_PO4 <- okokyst_plot(data = VR31, varname = "PO4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("PO"[4]), colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
                      #theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))

VR31_PO4

#ggsave ("Figures/VR31/VR31_PO4.png", dpi=500, , width = 8, height = 3)
```

####VR31 TOTP
```{r}
quantile (VR31$TOTP, na.rm = T)

# med punkter

grenser <- c(0,60)
VR31_TOTP <- okokyst_plot(data = VR31, varname = "TOTP", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTP", colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", labels =  NULL)

VR31_TOTP

#ggsave ("Figures/VR31/VR31_TOTP.png", dpi=500, width = 8, height = 3)
```


####VR31 SIO2

```{r}

quantile (VR31$SIO2, na.rm = T)

# med punkter
grenser <- c(0,900)
VR31_SIO2 <- okokyst_plot(data = VR31, varname = "SIO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("SiO"[2]), colours = jet.colors(16),limits=grenser,breaks = c(200,400,600,800), oob=squish ) +
                       scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR31_SIO2

#ggsave ("Figures/VR31/VR31_SIO2.png", dpi=500, width = 8, height = 3)

```

##cOMBINE 
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
VR31_fosfat <- VR31_TOTP +  VR31_PO4 +  plot_layout(ncol = 1,  width = 8, height = 6)
plot (VR31_fosfat)
ggsave("Figures/VR31/VR31_fosfat_panel_longtimeseries.png", plot = VR31_fosfat,  width = 8, height = 6)
```
  

#### VR31 klfa
```{r}
quantile (VR31$KlfA, na.rm = T)

# med punkter
grenser <- c(0,5)
VR31_KlfA <- okokyst_plot(data = VR31, varname = "KlfA", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                      scale_fill_gradientn("KlfA", colours = jet.colors(16),limits=grenser, breaks = c(1,2,3,4), oob=squish) +
                      scale_x_datetime(date_breaks = "4 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR31_KlfA 

ggsave ("Figures/VR31/VR31_KlfA_longtimeserie.png" , width = 8, height = 3)
```


``{r}
```



#### VR61 TOTN
```{r}

# check range, can be set automatically, but I often found the plot looks nicer if you set manually
quantile(VR61$TOTN, na.rm = T)

# with colored points and date label every 2nd month (depends on length of the timeseries for the station)
# NB! here I set the labels = null (compare with VT71 below), because I want to have them on top of eachother in a panel (see 3. Combine figures below)

grenser <- c(0,500)
VR61_TOTN <- okokyst_plot(data = VR61, varname = "TOTN", ctd_variable = F,
                   colored_points = T, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTN", colours = jet.colors(20), limits= grenser, breaks = c(100,200,300,400), oob=squish) +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR61_TOTN

ggsave ("Figures/VR61/VR61_TOTN.png", dpi=500, width = 8, height = 3)


```



#### VR61 NO3
```{r}

quantile (VR61$NO3_NO2, na.rm = T)

# med punkter

grenser <- c(0,200)
VR61_NO3 <- okokyst_plot(data = VR61, varname = "NO3_NO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits =grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NO"[3]* "+ NO"[2]), colours = jet.colors(16), limits = grenser, breaks = c(50,100,150), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR61_NO3

ggsave ("Figures/VR61/VR61_NO3.png", dpi=500, width = 8, height = 3)
 
```
#### VR61 NH4
```{r}

quantile (VR61$NH4, na.rm = T)

# med punkter
grenser <- c(0,80)
VR61_NH4 <- okokyst_plot(data = VR61, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NH"[4]), limit=grenser, colours = jet.colors(16), breaks = c(20,40,60), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR61_NH4

ggsave ("Figures/VR61/VR61_NH4.png", dpi=500, width = 8, height = 3)


```


####


## 3. Combine figures (with patchwork library)
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
Nitrogen <- VR61_TOTN +  VR61_NO3 + VR61_NH4 + plot_layout(ncol = 1, width = 8, height =6)
plot (Nitrogen)
  ggsave("Figures/VR61/VR61_nitrogen_panel_test.png", plot = Nitrogen,  width = 8, height = 6)
  
```

####VR61 PO4

```{r}

quantile (VR61$PO4, na.rm = T)

# med punkter

grenser <- c(0,60)
VR61_PO4 <- okokyst_plot(data = VR61, varname = "PO4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("PO"[4]), colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)
 
                      #theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))

VR61_PO4
ggsave ("Figures/VR61/VR61_PO4.png", dpi=500, , width = 8, height = 3)
```

####VR61 TOTP
```{r}
quantile (VR61$TOTP, na.rm = T)

# med punkter

grenser <- c(0,60)
VR61_TOTP <- okokyst_plot(data = VR61, varname = "TOTP", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTP", colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR61_TOTP

ggsave ("Figures/VR61/VR61_TOTP.png", dpi=500, width = 8, height = 3)
```


####VR61 SIO2

```{r}

quantile (VR61$SIO2, na.rm = T)
rm
# med punkter
grenser <- c(0,900)
VR61_SIO2 <- okokyst_plot(data = VR61, varname = "SIO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("SiO"[2]), colours = jet.colors(16),limits=grenser,breaks = c(200,400,600,800), oob=squish ) +
                       scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR61_SIO2

ggsave ("Figures/VR61/VR61_SIO2.png", dpi=500, width = 8, height = 3)

```

##cOMBINE 
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
VR61_fosfat_Si <- VR61_TOTP +  VR61_PO4 + VR61_SIO2 +  plot_layout(ncol = 1,  width = 8, height = 6)
plot (VR61_fosfat_Si)
ggsave("Figures/VR61/VR61_fosfat_Si_panel.png", plot = VR61_fosfat_Si,  width = 8, height = 6)
```
  

#### VR61 klfa
```{r}
quantile (VR61$KlfA, na.rm = T)

# med punkter
grenser <- c(0,5)
VR61_KlfA <- okokyst_plot(data = VR61, varname = "KlfA", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                      scale_fill_gradientn("KlfA", colours = jet.colors(16),limits=grenser, breaks = c(1,2,3,4), oob=squish) +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR61_KlfA 

ggsave ("Figures/VR61/VR61_KlfA.png" , width = 8, height = 3)
```




#### VR52 TOTN
```{r}

# check range, can be set automatically, but I often found the plot looks nicer if you set manually
quantile(VR52$TOTN, na.rm = T)

# with colored points and date label every 2nd month (depends on length of the timeseries for the station)
# NB! here I set the labels = null (compare with VT71 below), because I want to have them on top of eachother in a panel (see 3. Combine figures below)

grenser <- c(0,500)
VR52_TOTN <- okokyst_plot(data = VR52, varname = "TOTN", ctd_variable = F,
                   colored_points = T, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTN", colours = jet.colors(20), limits= grenser, breaks = c(100,200,300,400), oob=squish) +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR52_TOTN

ggsave ("Figures/VR52/VR52_TOTN.png", dpi=500, width = 8, height = 3)


```



#### VR52 NO3
```{r}

quantile (VR52$NO3_NO2, na.rm = T)

# med punkter

grenser <- c(0,200)
VR52_NO3 <- okokyst_plot(data = VR52, varname = "NO3_NO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits =grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NO"[3]* "+ NO"[2]), colours = jet.colors(16),limits=grenser, breaks = c(50,100,150), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR52_NO3

ggsave ("Figures/VR52/VR52_NO3.png", dpi=500, width = 8, height = 3)
 
```
#### VR52 NH4
```{r}

quantile (VR52$NH4, na.rm = T)

# med punkter
grenser <- c(0,80)
VR52_NH4 <- okokyst_plot(data = VR52, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("NH"[4]), limit=grenser, colours = jet.colors(16), breaks = c(20,40,60), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR52_NH4

ggsave ("Figures/VR52/VR52_NH4.png", dpi=500, width = 8, height = 3)


```


####


## 3. Combine figures (with patchwork library)
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
Nitrogen <- VR52_TOTN +  VR52_NO3 + VR52_NH4 + plot_layout(ncol = 1, width = 8, height =6)
plot (Nitrogen)
  ggsave("Figures/VR52/VR52_nitrogen_panel_test.png", plot = Nitrogen,  width = 8, height = 6)
  
```

####VR52 PO4

```{r}

quantile (VR52$PO4, na.rm = T)

# med punkter

grenser <- c(0,60)
VR52_PO4 <- okokyst_plot(data = VR52, varname = "PO4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("PO"[4]), colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)
 
                      #theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))

VR52_PO4

ggsave ("Figures/VR52/VR52_PO4.png", dpi=500, , width = 8, height = 3)
```

####VR52 TOTP
```{r}
quantile (VR52$TOTP, na.rm = T)

# med punkter

grenser <- c(0,60)
VR52_TOTP <- okokyst_plot(data = VR52, varname = "TOTP", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TOTP", colours = jet.colors(16), limits=grenser, breaks = c(10,20,30,40,50), oob=squish) +
                      scale_x_datetime(date_breaks = "2 month", labels =  NULL)

VR52_TOTP

ggsave ("Figures/VR52/VR52_TOTP.png", dpi=500, width = 8, height = 3)
```


####VR52 SIO2

```{r}

quantile (VR52$SIO2, na.rm = T)

# med punkter
grenser <- c(0,900)
VR52_SIO2 <- okokyst_plot(data = VR52, varname = "SIO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn(name= expression("SiO"[2]), colours = jet.colors(16),limits=grenser,breaks = c(200,400,600,800), oob=squish ) +
                       scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR52_SIO2

ggsave ("Figures/VR52/VR52_SIO2.png", dpi=500, width = 8, height = 3)

```

##cOMBINE 
```{r}
# combine figures, here combine two NO3 for different stations
#NB can of curse combine different variables for one station as well 
VR52_fosfat_Si <- VR52_TOTP +  VR52_PO4 + VR52_SIO2 +  plot_layout(ncol = 1,  width = 8, height = 6)
plot (VR52_fosfat_Si)
ggsave("Figures/VR52/VR52_fosfat_Si_panel.png", plot = VR52_fosfat_Si,  width = 8, height = 6)
```
  
```
#### VR52 klfa
```{r}
quantile (VR52$KlfA, na.rm = T)

# med punkter
grenser <- c(0,5)
VR52_KlfA <- okokyst_plot(data = VR52, varname = "KlfA", ctd_variable = FALSE,
                   colored_points = TRUE, limits = grenser, binwidth = 20, max_timediff = 25, ylabel = F, xlabel = F) +
                      scale_fill_gradientn("KlfA", colours = jet.colors(16),limits=grenser, breaks = c(1,2,3,4), oob=squish) +
                      theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR52_KlfA 

ggsave ("Figures/VR52/VR52_KlfA.png" , width = 8, height = 3)
```

```{r echo=FALSE}
save.image (file = "Plots_contour_NHs.Rdata")
```
