---
title: "Rean and check a file downloaded from Aquamonitor"
author: "Helene Frigstad"
date: "18 february 2021"
output: html_notebook
---

## 0. Libraries
```{r}
library(tidyverse)
library(readxl)
#library(pander)
#library(scales)
#library(gridExtra)
#library(grid)
#library (caTools)
#install.packages("xlsx")
#library(xlsx)
library (lubridate)

```


## 1. Folders and files    
Content of folders (see code)  
* R markdown must have working directory in same location as the script file is stored, ie. put data and script in same overall folder
```{r}
#clear workspace if needed
#ls()
#rm(list = ls())

# sjekke filer i folder "Datasett"
dir("Datasett")
```

## 2. Read and clean files

### a. read
* Reads file downloaded from Aquamonitor 15.02.2022, excel-file was cleaned before reading into R (ToR.xlsx), see the  the Dir command above for the two excel files 
* In the ToR version I did following changes: 1. deleted row with units (paste into script below) and have all column heads in one top line. 2. Separate Date into 4 separate columns (day, Month, Year, Time), using the text-to-columns in excel. 3. Removed all values below detection limit (ex Klfa < 0.16), by using excel replace (find: <*, replace: (just a space))
```{r}
#? read_excel
df <- read_excel("Datasett/AqM_data_2022_02_15_12_20_ToR.xlsx", "WaterChemistry", col_names = T, col_types = c("text", "text", "text", "text", "text", "text","text","text","text", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric"))  


#units (pasted in from excel file)
#DOC	Fluorescens	KlfA	NH4-N	Nitrogen part	NO3+NO2-N	O2	O2	O2 (metning)	PO4-P	POC	P-PO4	Salinitet	SGR - Suspendert gløderest	Siktdyp	SiO2	STS	Temperatur	Tetthetsanomali	TOTN	TOTP	TOTP_P	TSM	Turbiditet
#mg/L C	µg/l	µg/l	µg/l	µg/l N	µg/l	mg/L	ml/l	%	µg/l	µg/l C	µg/l P		mg/l	m	mg/l	mg/l	C	kg/m3	µg/l	µg/l	µg/l P	mg/l	FNU


#lage datoobjekt fra de tre kolonnene Year, Month, Day
df$Date <- as.Date (paste (df$Year, df$Month, df$Day, sep ="-"))

#summary (df)
#tr(df)

```


### b. clean
```{r}

# stationID is consistent across projects and time (this can vary for different projects) 
df$StationId <- as.factor (df$StationId)
#(as.factor (df$StationId))
#df$StationId <- as.factor (df$StationId)
#levels(df$StationId) #"63018" (VT71) "68915" (VT16) "68936" (VT3) "68938" (VR54) "68992" (VR21) "70953" ()

# rename StationID from numeric to station code
sel <- levels(df$StationId) == "63018"; sum(sel)
levels(df$StationId)[sel] <- "VT71"
sel <- levels(df$StationId) == "68936"; sum(sel)
levels(df$StationId)[sel] <- "VT3"
sel <- levels(df$StationId) == "68938"; sum(sel)
levels(df$StationId)[sel] <- "VR54"
sel <- levels(df$StationId) == "68915"; sum(sel)
levels(df$StationId)[sel] <- "VT16"
sel <- levels(df$StationId) == "68992"; sum(sel)
levels(df$StationId)[sel] <- "VR21"
sel <- levels(df$StationId) == "70953"; sum(sel)
levels(df$StationId)[sel] <- "VR58"

# order stations for ggplot, here south to north
df$StationId <- factor(df$StationId, levels = c("VT3", "VT16", "VT71", "VR54", "VR58", "VR21"))

#include only data from 2017 to 2021 (or just 2020?)
#range (df$Date)
df <- subset(df, Date >= "2017-01-01" &  Date <= "2021-12-31")

# unique values? removed duplicated rows
df <- distinct (df)



# keep only relevant cols and rename
#str(df)
df_sel <-  select (df, StationId, Date,  Depth1,  Depth2, Salinitet, Temperatur, Siktdyp, Turbiditet, DOC, KlfA, O2_mg, O2_ml, NO3_NO2, NH4, PO4, SiO2, TOTN, TOTP, POC, PN, PP, TSM)
#df_sel <- rename(df_sel, Salinitet = Saltholdighet)

# remove the two high DOC concentrations (see below), but retain all rows that have NA
df_sel2 <- df_sel %>% filter((DOC < 5)  %>% replace_na(TRUE))


#remove duplication of rows due to multiple projects
df_sel3 <- distinct (df_sel2)

#str(df_sel)

```

## 2. Exploratory plots 

### a. Boxplots
```{r}
# look at ranges
ggplot(df, aes(DOC, fill = StationId)) + 
  geom_boxplot() 

#Use this if you want to save, notice that have Figures/... to save it in the right folder under the Oceanography-toolbox main folder
#ggsave ("Figures/Boxplot_DOC_fullrange.png", width = 8, height = 6, dpi=500)


ggplot(df_sel2, aes(DOC, fill = StationId)) + 
  geom_boxplot() 

#ggsave ("Figures/Boxplot_DOC_below5.png", width = 8, height = 6, dpi=500)

ggplot(df_sel2, aes(Salinitet, fill = StationId)) + 
  geom_boxplot() 

ggplot(df_sel2, aes(Temperatur, fill = StationId)) + 
  geom_boxplot() 

ggplot(df_sel2, aes(NH4, fill = StationId)) + 
  geom_boxplot() 

ggplot(df_sel2, aes(TSM, fill = StationId)) + 
  geom_boxplot() 

#ggsave ("Figures/Boxplot_TSM.png", width = 8, height = 6, dpi=500)

ggplot(df_sel2, aes(POC, fill = StationId)) + 
  geom_boxplot() 

#ggsave ("Figures/Boxplot_POC.png", width = 8, height = 6, dpi=500)

# one high obs of 270 for VR54 - remove above 100?
ggplot(df_sel2, aes(PN, fill = StationId)) + 
  geom_boxplo
  geom_boxplot() 




```

## 3. Save
```{r}

# on my computer, this is the location of the folder to save datasets in: C:\Data\Helene_Work\Oceanography-toolbox\Oceanography-toolboxC:/Data/Helene_Work/OKOKYST_2021_25/OKOKYST-Klima/Datasett

# tab-delimited text file 
write.table(df_sel3, "Datasett/OKOKYST_data_cleaned.txt", sep="\t")
# comma separated
write.csv(df_sel3, file = "Datasett/OKOKYST_data_cleaned.csv")


```				 			




